% ╒══════════════════════════════════════════════════════════════════════════╕ %
% │                                CHAPTER  1                                │ %
% ╘══════════════════════════════════════════════════════════════════════════╛ %
\ifdm
    \chapter{Concept}
    \label{concept}

    \DndDropCapLine{A}{s a peasant it's important to be doing} something. In our case it would be to be an alchemist and herbalist. Knowing plants and fungi around the realm is the bread and butter of the character.

    \section{Goliath} 
    We're a goliath that has been brought up by goliath parents, however not brought up in a goliath tribe dampened some of the goliath 'norms'. Still thinking fair play, self sufficiency and being pragmatic.

    \subsection{Being pragmatic}
    Light mockery and a bit of passive aggressiveness is something that might be used to mock unfit leaders or choices that "don't make sense".

    \section{Profession}
    The character starts mostly as a herbalist and aspiring alchemist. Knowing some (very) common plants, herbs and fungi is important for the character as well as knowing (some) use cases for them.

    \subsection{Inspiration}
    Inspiration will be drawn from the works of "Hammund's harvesting guide" and "Broderick's Compendium: Plants and Fungi across the realm". They will be used mainly for flavour as we do not want to burden the game with mechanics.

    \section{Attitude and character}
    A not so strong goliath needed to be quick witter, smart and thoughtful. Learning by experimenting and from one of his parents experience gave the character an edge.

    Usually very well composed but quick to get annoyed when people make fun of his quirks.

    \subsection{Quirks}
    From a failed experiment he has permanent hiccups. They can be suppressed for a relative 'short' while, by a concoction of Anise. When not being suppressed he has disadvantage on stealth checks or some charismatic checks, depending on the situation.

    \section{Background}
    Raised by goliath parents living a 'nomadic' lifestyle. 
    They made a living by gathering plants, fungi and herbs.
    The character used these opportunities to study herbs, plants and fungi in different libraries o 
    Settled after the fathers death while the father kept going after being struck by illness.
    Mother started a tiny alchemy shop, near Heronbride, where the character picked up some traits.
    Feeling restless, the character decided to move, ending up in Ravenspire and buying a run down cottage.

    During the travels he was able to make some contacts and also discovered that he and his family were actually refugees from a war. Knowing this hurt his pride somewhat. The only information the character has is a faint location, a rumoured direction they might have gone and a tribe name.

    \section{Aimed progression}
    The aimed progression would be mainly in the profession. Adventuring is well and good, but where I see this character going is as a decently well known herbalist and alchemist. The class that fits best is an artificer (alchemist)

    Ultimately I would want to send players to fetch specific materials for some more daring crafts/experiments. Not only potions/tonics but also infused items (again, using Hammund harvesting guide as an inspiration)

    \section{Appearance}
    Vararhak is a tall, athletic Goliath. Compared to other Goliaths however, he's less muscular. With his tough brown-copper skin and bright green eyes you can't help but notice the bald head and distinct and hard eyebrow ridge. Besides other facial features you notice a small braided black beard. On his jaw you notice a bone or skin growth the size of a small coin.

    Usually donned in Studded leather armour with a sickle visible and bunches of herbs, plants and other vegetation on his belt. He looks surprisingly well kept with clean armour and clothes.


    Did he actually stop having the hiccups while you were looking at him?
\fi