% ╒══════════════════════════════════════════════════════════════════════════╕ %
% │                                CHAPTER  2                                │ %
% ╘══════════════════════════════════════════════════════════════════════════╛ %
\chapter{Vararhak backstory}
\label{background}

\DndDropCapLine{V}{ararhak Roothand was not a normal} goliath. Growing up with his nomadic parents he did get some of the goliath values and characteristics, but not as a full grown tribesman would.

\section{Growing up}
As he grew up with his parents, they travelled from place to place. Living of the land and selling gathered plants, herbs and fungi in villages or cities. Whenever Vararhak was able to learn something about these plants he would seize the opportunity.

Keeping a detailed sketchbook of the vegetation, he was able to catalogue some of the more uncommon specimen's on his travels, not necessarily knowing the use or name of these plants.

His mother, Orine Plantgrinder, knew how to make use of some of these gathered materials. Being intrigued by the process Roothand picked up some knowledge and started experimenting.

On a faithful day one of his experiments went wrong. Being a reckless teenager he created a tea out of some herbs he never saw before, having excruciating cramps the following hours. After the pain subsided, Roothand was left with the hiccups, hiccups he still has till this very moment.

\section{His father's death}
After his father passed, due to illness and stubbornness, Orine and Vararhak settled just north of Heronbridge. Orine set up an alchemy and herbalist shop where Roothand learned most of the more commercial uses of his skills.

Being restless, Vararhak moved on and became a nomad once more.

% \section{Settling near Ravenspire}
% After a few years of travelling and studying. Vararhak decided to settle in a small run down cottage an hour away from Ravenspire. Just like his mother he set up a small shop, selling some plants, herbs, fungi and concoctions of his making.

\section{Meeting Xion Bronzeheart}

On his travels Vararhak met Xion Bronzeheart, another alchemist. Helping each other with gathering materials they decided to travel together. Roothand was able to show Xion a few tips and tricks that he in his turn learned from his mother.

Around Ravenspire, they heard of a lucrative job offering from Butcher's farm. Xion easily convinced Vararhak to go and set up shop in Butcher's farm. On their journey to Butcher's farm Vararhak learned that his parents were from the Agu-Vigala tribe and refuges from a war close to Northgate, rumoured to be going east. This information burdened Vararhak and hurt his pride. They decided against the warn-torn area for now and set up shop at the edges of Canton instead.
