% ╒══════════════════════════════════════════════════════════════════════════╕ %
% │                                CHAPTER  3                                │ %
% ╘══════════════════════════════════════════════════════════════════════════╛ %
\chapter{Vararhak and Xion's cottage}
\label{shop}

\DndDropCapLine{P}{lants and potions is Vararhak and} Xion's little (work)shop they set up. 
A small but cozy cottage just fitting both of them with separate rooms. It seems a bit run down, but Xion and Vararhak are patching the place up. Mostly made out of stone and wood it has a very homily feeling to it. Because of the plants it has a very fresh, but acidic smell to it.

\section{Plants and Potions}
A stall with a tarpaulin roof covered with climbing plants and other vegetation is standing in front of the biggest open window of the cottage. 

The stall is full of jars of dried and fresh herbs, fungi and plants, besides these jars there are pots with life plants. Only a few potions are being displayed on the stall.

% \begin{DndTable}[header=Vegetation]{XX}
%     Item  & Value \\
%     Anise  & 10cp
% \end{DndTable}

% \begin{DndTable}[header=Potions and Tonics]{XX}
%     Item  & Value \\
%     Hiccup remedy  & 15cp
% \end{DndTable}

\section{Inside the cottage}
The cottage is quite dim, but overly decorated with plants and other vegetation giving it a very fresh and pleasant smell. The alchemist workspace set up close to the big window does give a penetrating acidic tickle in your nose. 

Sporting a few separate workspaces, with alchemist and herbalist tools it seems well equipped for the novice craftsmen. What is noticeable is that the furniture is quite small or awkwardly large for most. The only other room has been divided between a loft covered by leaves just barely giving enough room for Xion, while the other has proper walls and a door for Vararhak.

\subsection{Vararhak's room}
When you enter you immediately see papers taped on the wall with different scientific sketches of plants, fungi and herbs. A writing desk with a chair, a bed and a chest are all in the room. On the desk is an unfinished drawing of what seems to be a strange moss-like climbing plant.
