% ╒══════════════════════════════════════════════════════════════════════════╕ %
% │                                CHAPTER  2                                │ %
% ╘══════════════════════════════════════════════════════════════════════════╛ %
\chapter{The gracious host}
\label{diary__gabriel}

\DndDropCapLine[]{W}{hen finding our bearing} after the escape, we met the most unlikely of hosts. He gave us tea after we sneaked into his mansion.

\section{The vampire host}

I was a bit pre-occupied and couldn't journal. I hope you don't mind \Master{}. But I have some exciting news. We met an interesting fellow, he did pique my interest. His name is Gabriel. He lives in a big mansion inside Tarreton, but I'm getting ahead of myself.

\subsection*{Black smoke}

It all started on the outskirts of the wall, Leon and I were a bit split up from the rest of the group. But when we arrived at the city, we saw Meirah, Kreek and Nevrest fighting on the walls, jumping down into a black smoke! We saw that it went into a big mansion in the city. Very cautious Leon and I sneaked to the living room where we found our friends. Trying to get them out they decided to stay and talk, claiming they knew where they were.

Anyhow, long story short, there was a butlers, who's name I forgot and the master, Gabriel. He gave us a task to retrieve a 'red flower' from the forest. It seems very easy, so it's probably not.

In his study, which I was allowed to use, don't worry \Master{}, I found a magical incantation and some supplies to test it out. I quickly copied it over to you, and you gave me some tips here and there.

I also went to the magic shop ****. The patron of that shop told me, if I stole tea from one lady named Lady Larrenhael, I could sell it to him for a big chunk of gold. I tried to swoop in with my raven, but it sadly got killed outright. Maybe she had a detect magic ward.

\subsection*{The road to the red flower}

When we met up in the city, heading towards the gate we got stopped by the warden, a female bronze dragonborn adorned with plate armour that is decorated with the city crest. She seemed to be quite upset at Nevrest and Meirah mentioning that they "disappeared all the evidence" and that "she'll keep an eye out on them and your friends". So Leon and I got caught in the crossfire of this vendetta.

It was however a quite beautiful day to be walking towards the forest. It did get interrupted by a scream. A feline woman was being held up by 4 pieces of scum that ran away once they noticed us. Once we dealt with them, 2 of the corpses combusted while the other 2 were unconscious. The scoundrel had a note describing the Tabaxi. While we were questioning them, one of them touched a snake tattoo that went up his neck and bit him, making him burst out in flames. The other guy wanted to follow but, surprising myself, I quickly grabbed a scimitar laying on the floor and cut of his arm.

We tended to the man, who seemed to be very angry and in pain. I imagine this is one of these "fail-safe tattoo's" you once told me about. The one that criminals use so no information get out by destroying the body. Anyhow, this tattoo was in the form of a snake and the man said it was from a group called "The pythons".

The woman is a herbalist (that didn't hear of the particular red flower) who goes by the name of Wintermoon. She didn't know why the Pythons are after her. She was travelling from Gravesford to Tarreton to visit her adoptive father, Marcus Silverstein, The travelling merchant. She also wants to study alchemy under a woman called Pinna.

Nevrest was able to squeeze some information out of the arm-less bandit, mainly that he's working for "Alsira" and a job to stop Wintermoon from getting to the city.

I just woke up from a night terror again. Seems Kreek and the rest of the companions also had some bad dreams, I'll keep you posted.

\subsection*{The red flower}
The day started after we all woke from those harrowing dreams. We managed to find the path described by Gabriel, our undead host. We found a stone house with a nice picket fence, full of flowers in her garden.

When Leon went up to talk to the nice old lady, Meirah informed us that it's a 'Night hag', an evil magic user that haunts your dreams and tries to invite you in. Leon almost went inside the house for tea and cookies.

We planned a 'flower' heist. Knowing it was dangerous we used a bag to grab as many as we could. The whole group stayed on the edge of my teleportation spell. I made Leon invisible, he went to grab the flowers and the second he did, magical bolts were flying to my face. I teleported Leon and stepped into the void myself and we bolted. We were able to run away, but I was wounded. We had 3 flowers in our possession.

When we got back to Gabriel, he couldn't tell us about why he needed the flower, or who the Pythons were.

As a reward he gave me a book where I can see 3 incantations. I was able to make out it's about seeing invisibility, shaping water and some protection against good and evil. I however don't have the required ink to let you know.