% ╒══════════════════════════════════════════════════════════════════════════╕ %
% │                                CHAPTER  2                                │ %
% ╘══════════════════════════════════════════════════════════════════════════╛ %
\chapter{Meeting the lady}
\label{diary__maerwynn}

\DndDropCapLine[]{P}{eace and freedom} need your help. That's quite the statement to make to a group of adventurers. Lets see what peace and freedom can do for us.

\section{Meeting the lady}
\subsection*{The unstoppable manticore}
We arrived at the inn and Meirah knocked on one the big door, existing of multiple parts and blue eyes emerge from a just created slit in the door. We met who later turned out to be Lincoln, adorned in fine robes and a scar over his eye. He gave us the first room after the stairs. We also called ourselves BlitzKreek, it seemed fitting with Kreek.

Our room was nothing special, we had a few beds, just enough for all of us, besides Kreek.

For breakfast, we got some bread and cheese. We talked about Mallec of Ashor with Lincoln, who laughed at us and told us he's a fool with a stupid magic show swindling people with cheap magic.

I was trying to solve the puzzle but couldn't figure it out until Leon pointed out the obvious. It bothered me a bit that he was able to solve the, in hindsight, fairly obvious code. When giving Lincoln the code, we received a key that manifested from his tattoo to meet the mysterious lady in the cellar.

\begin{DndReadAloud}
    While trying to solve the puzzle I figured out that Lincoln the innkeeper's arm and back are magical, and that there is a magical glaive under his counter!
\end{DndReadAloud}

\subsection*{The cellar}
Outside the tavern there was a double door leading to the cellar. A storage room with stacked barrels. I was able to find a keyhole next to the pyramid of barrels which opened up a passage way where we met the most curious of people.

Two elves in the meeting room, together with a dwarf. One of the elves face is covered in a hood, while the other had long dark and smooth hair, hands on both her daggers and a tense posture ready to spring in action.

The hooded elf reveals herself as Lady Maerwynn, ruler and baroness of Taeris. She says that she needs our help for 'peace and freedom'.

\begin{DndReadAloud}
    Lady Maerwynn is the ruler of Taeris.
\end{DndReadAloud}

She explains that the baron of Bedegar got killed but ruled as a tragic accident with no foul play or something alike. There is no official investigation and that's where we come in. Leon was apparently in the army for this baron.
A group of white-fanged orcs invaded the castle, killing the whole family, leaving no heir. Only commander and chief, General Saxton, survived. He now rules over the county as General and Commander of Ashors military.
General Saxton wasn't a supporter of the peace between the counties and you cannot voice your concerns. General Saxton rules with oppression and there is no proof or investigation where he lead the coup against the Baron of Bedegar.
She told us several people were abducted and that it might have been part of the suspected coup.

\begin{DndReadAloud}
    Leon even explains how his company and a lot of others got sent away as training, just before the attack. General Saxton was conveniently away on training too.
\end{DndReadAloud}

The reason why she singled out our group is because she cannot send her army here and we seem to possess what's needed to full-fil this mission. We are also not the first group she sent out.

Besides gold and riches, the lady promised to get me into the academy, as her recommendation would come a long way. Nevrest asked for a 'specific' person to be delivered, he has an "itch". He creeped everyone out...

\section{(Un-)official agents of Taeris}
\Master{}, BlitzKreek are now agents of Taeris. I'm not sure what this would mean for me or \Cloister{} but I will make sure they can get support if it ever needs it!

\begin{DndTable}[header=The three lieutenants]{XX}
    \textbf{Place}  & \textbf{New position} \\
    Sir Pelliton    & Ruler of Gravesford \\
    Lady Ruth       & Ruler of Tarreton \\
    Sir Barlow      & Commander of the Marine and Sea Forces
\end{DndTable}

Lady Maerwynn suggested we start our investigation in the east of Gravesford, as it's strange it's got his own ruler, being a 'very' small village.

\subsection*{Personal favour}
The baroness wanted something else from us, \Master{}. We wouldn't be the first one to investigate this and she wants us to found out what happened to her dear friends and allies. Could you believe it, first setting us on a task and then telling us some others already went missing. I noted down the description from all five.

\DndFeatHeader{Durhelim Galatogtle}[Paladin in the Order of the Lightseeker]
a middle aged Human Paladin that was trained as a diplomat and Mediator.

\DndFeatHeader{Alex Gaarder}[Cleric of Kelemvor]
human cleric that is a close friend and trusted adviser for her and grave keeper of the royal family crypt.

\DndFeatHeader{Monty W. Featherpunch}[Noble Gentleman Adventurer]
Elven middle aged Gentlemen and part of the Taeris Aristocratic Society. He always talked about going on an adventure and now finally got the chance

\DndFeatHeader{Bree Copperkettle}[The Quick Hands and Mouth]
a young halfling that had the street-smarts. Informant for the Lady and access to the "greyer" parts of society

\DndFeatHeader{Hjaldar}[The Muscle and intelligence specialist]
a dwarven trainee of the Taeris Military and Intel gather

\subsection*{Contacting our patron}
Before the meeting was adjourned, the baroness told us we could talk to Lincoln, the innkeeper. When we left the meeting room, the keyhole disappeared.

\begin{DndReadAloud}
    I still had my detect magic on. Almost everything in the room was glowing. Notably the dwarf and Lady Maerwynn were glowing, the other elf not. The daggers of the non-glowing elf however, were bright as the sun. The book the dwarf was holding, I was able to discern a different glow.
\end{DndReadAloud}